### 2019-10-11 related.tex
related work commit

\section{Related Work}
\label{sec:related}
In this section, we present tools and techniques
that partially address the limitations of navigating
spreadsheets as discussed in the introduction.

\subsection{Spreadsheet Tools and Prototypes}
\cut{Commercial spreadsheet tools include
Microsoft Excel, Google Sheets, and Airtable---of
these, Excel and Google Sheets support features
targeted at improving users' navigation experience.}

\cut{Excel allows users to maintain context during navigation
by manually creating named ranges~\cite{named-range},
that are essentially references
to a spreadsheet region,
and appear in a \emph{name box}
within the Excel menu bar.
Users can click on a named range
to navigate to the referred region.
However, the onus is on the user to create
named ranges for each region of interest.}
\stitle{Microsoft Excel.}
\saj{Excel enables users to manually create references
to a spreadsheet region using the named ranges~\cite{named-range} feature which is displayed within the Excel menu bar.
Users can click on a named range
to navigate to the referred region. However, the onus is on the user to create
named ranges for each region of interest. The Pivot table~\cite{pivot} feature provides a summary view, enabling users
to compare subsets of data without
having to navigate to various locations
within the spreadsheet.
This summary is placed
in a separate region in the spreadsheet,
preventing users from accessing
the data underlying the summary, thereby, impeding navigation. A similar overview feature, \code{SUBTOTAL}~\cite{subtotal},
adds a new row at the end of the
corresponding subset of data with summary
information. Users can expand the summary to view
the actual spreadsheet data.
However, for datasets with larger subsets (\eg for numeric data),
the size of the summary can become very
large spanning multiple screens and can cause
increased
visual discontinuity during navigation. Finally, NodeXL~\cite{hansen2010analyzing}
is an Excel plug-in that provides an overview
of a network
and enables users to perform navigational operations,
\eg zooming in/out, dynamic filtering, on the overview;
this plugin only supports network datasets,
such as biological or social networks.}

@@

\stitle{Scalable Spreadsheet Summarization and Exploration.}
Smart-drill-down~\cite{joglekar2015smart}
generates an interactive summary of a large spreadsheet table as
a collection of rules; users can drill-down to
a specific rule to view more fine-grained rules.
Hillview~\cite{web:hillview} displays
the results of group-by queries
on large spreadsheet tables.
While these tools support summarization at scale,
providing an overview of the spreadsheet,
they don't preserve spreadsheet semantics,
nor do they make it easy to scroll or steer
through large spreadsheets.
ABC~\cite{Raman99scalablespreadsheets} and {\sc DataSpread}~\cite{datamodels} support interactive
exploration of very large spreadsheet datasets,
beyond main-memory limits, maintaining spreadsheet look-and-feel,
but do not provide any new spreadsheet capabilities to assist
with navigation.
We build \noah as a plugin
to {\sc DataSpread}, since it is open-source.

@@

\stitle{Tabular Data Analysis (TDA).}
Visualization tools such as Tableu~\cite{tableau}, Power BI~\cite{powerbi}, Keshif~\cite{yalccin2018keshif}, Voyager~\cite{wongsuphasawat2016voyager} and
analytical tools such as SPSS~\cite{noruvsis1986spss}, SAS~\cite{sas1985sas}, can all provide summaries of tabular data in various forms (visualizations,
aggregate statistics). 
\saj{However, these summaries 
are static overviews of the data---much like pivot tables, 
these summaries are not dynamically linked
to nor are co-located with
the underlying data. 
Naturally, 
users cannot navigate and directly manipulate the raw data
using these tools unlike spreadsheets. For example, using these tools users cannot \code{browse} subsets of data and \code{lookup} or \code{locate} data points of interest (see Table~\ref{tab:scope}). Even users of such tools want to inspect the underlying data to verify the summary statistics and visualizations~\cite{2017trust}.
%several wanted to be able to see the underlying data: although big data demands aggregations, analysts wanted to see individual records to spot-check their results, and to get a sense of what sat in a bucket. 
The goals of spreadsheets vary from the TDA tools in two different ways: a) facilitating direct manipulation of the data and b) enabling arbitrary derivation of new data and summaries
using various operations involving navigation,
\eg formulas or expressions.
\noah being a plugin to spreadsheets, facilitates a unified interface that
upholds both these goals
while enhancing
the navigational capabilities
for spreadsheet users.
}

>>>>

%!TEX root = main.tex

\section{Related Work}
\label{sec:related}
We now discuss tools and techniques
that partially address the limitations of navigating
spreadsheets.

\subsection{Spreadsheet Tools and Prototypes}
\cut{Commercial spreadsheet tools include
Microsoft Excel, Google Sheets, and Airtable---of
these, Excel and Google Sheets support features
targeted at improving users' navigation experience.}
\agp{Abrupt, add at least one line to say that existing spreadsheet tools recognize challenges in nav or something}

\cut{Excel allows users to maintain context during navigation
by manually creating named ranges~\cite{named-range},
that are essentially references
to a spreadsheet region,
and appear in a \emph{name box}
within the Excel menu bar.
Users can click on a named range
to navigate to the referred region.
However, the onus is on the user to create
named ranges for each region of interest.}
\stitle{Microsoft Excel.}
\new{Excel enables users to manually create references
to a spreadsheet region using the named 
ranges~\cite{named-range} feature,
accessible from the menu bar.
Users can click on a named range
to navigate to the referred region. 
However, the onus is on the user to create
named ranges for each region of interest. 
The pivot table~\cite{pivot} feature 
allows users to create a summary view to 
compare subsets of data without having to 
provides a summary view, enabling users
to compare subsets of data without
having to navigate to various locations
within the sheet.
This summary is placed
in a separate region of the spreadsheet,
preventing users from accessing
the data underlying the summary, impeding navigation. 
A similar overview feature, \code{SUBTOTAL}~\cite{subtotal},
adds a new row at the end of each distinct
subset of data with summary
information. Users can expand the summary to view
the actual spreadsheet data.
However, for datasets with many subsets (\eg for numeric data),
the number of new lines inserted (i.e., the summary) 
can itself become very
large, spanning multiple screens, and can cause
increased
visual discontinuity during navigation. Finally, NodeXL~\cite{hansen2010analyzing}
is a plug-in that provides a spreadsheet network overview
and supports navigational operations,
\eg zooming in/out, dynamic filtering, on the overview;
this plug-in only supports network datasets,
such as biological or social networks.}

@@

\stitle{Scalable Spreadsheet Summarization and Exploration.}
Smart-drill-down~\cite{joglekar2015smart}
generates an interactive summary of a large spreadsheet table as
a collection of rules; users can drill-down to
a specific rule to view more fine-grained rules.
Hillview~\cite{web:hillview} displays
the approximate results of group-by queries
on large spreadsheet tables.
While these tools support summarization at scale,
providing an overview of the spreadsheet,
they don't preserve spreadsheet semantics,
nor do they make it easy to scroll or steer
through large spreadsheets.
ABC~\cite{Raman99scalablespreadsheets} and {\sc DataSpread}~\cite{datamodels} support interactive
exploration of very large spreadsheet datasets,
beyond main-memory limits, maintaining spreadsheet look-and-feel,
but do not provide any new spreadsheet capabilities to assist
with navigation.
We build \noah as a plugin
to {\sc DataSpread}, since it is open-source.

@@

\stitle{Tabular Data Analysis (TDA).}
Visualization tools such as Tableu~\cite{tableau}, Power BI~\cite{powerbi}, Keshif~\cite{yalccin2018keshif}, Voyager~\cite{wongsuphasawat2016voyager} and
analytical tools such as SPSS~\cite{noruvsis1986spss}, SAS~\cite{sas1985sas}, can all provide summaries of tabular data in various forms (visualizations,
aggregate statistics). 
\new{However, these summaries 
are static overviews of the data---much like pivot tables, 
these summaries are not dynamically linked
to nor are co-located with
the underlying raw data. 
As such, the spreadsheet look-and-feel is lost,
and as a result, users
cannot navigate and directly manipulate the raw data
in the way they do in spreadsheets. 
For example, using these tools users cannot \code{browse} subsets of data and \code{lookup} or \code{locate} data points of interest (see Table~\ref{tab:scope}). \agp{previous line problematic: they can... because all these tools support to varying extents the typology}
Even users of such tools want to inspect the underlying data to verify the summary statistics and visualizations~\cite{2017trust}. \agp{this line is problematic too... because the citation is to an AQP tool rather than some general purpose study}
%several wanted to be able to see the underlying data: although big data demands aggregations, analysts wanted to see individual records to spot-check their results, and to get a sense of what sat in a bucket. 
The goals of spreadsheets differ from TDA 
tools in two ways: a) facilitating direct manipulation of raw 
data and b) enabling arbitrary derivation of new data and summaries
using various operations involving navigation,
\eg formulas or expressions.
\noah being a plug-in to spreadsheets, 
facilitates a unified interface that
upholds both these goals
while enhancing
navigational capabilities
for spreadsheet users.
}
